Concurrent Programming with CXL

### 2020-05-20 book/paper.tex
Latest
Explaining difference between atomic and locks

@@

@@

Locks are probably the most popular and basic form of synchronization
in concurrent programs.  For this reason, CXL has a module called
\texttt{synch} that includes support for locks.
Figure~\ref{fig:locks} shows how they are implemented, and
Figure~\ref{fig:lockme} gives an example of how they may be used.
Notice that the module completely hides the implementation of the
lock.

>>>>

It is important to appreciate the difference between an
\emph{atomic section} (the statements executed within an
\texttt{atomic} statement) and a \emph{critical section}
(protected by a lock of some sort).
The former ensures that while the
atomic statement is executing no other process can execute.
The latter allows multiple processes to run concurrently,
just not within the critical section.
The former is rarely available to a programmer, while the latter
is very common.

In CXL, atomic statements allow you to implement your own
low synchronization primites like test-and-set.  Atomic statements
are not intended to replace locks or other synchonization primitives.
By the way, CXL \texttt{assert} statements execute atomically
as if they are nested within an atomic statement.

@@

\chapter{Locks and the Synch Module}

@@

Locks are probably the most popular and basic form of synchronization
in concurrent programs.  For this reason, CXL has a module called
\texttt{synch} that includes support for locks.
Figure~\ref{fig:locks} shows how they are implemented, and
Figure~\ref{fig:lockme} gives an example of how they may be used.
Notice that the module completely hides the implementation of the
lock.
The \texttt{synch} module includes a variety of other useful
synchronization primitives, which will be discussed in later
chapters.
